### 2017-02-06 R/cambridge.Rmd
Update to cambridge.Rmd

```{r roadInjuries6, message = FALSE, , dev=c('png'), eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
simRI <- lapply(getRoadInjuries(ITHIM.baseline), function(x){
  lambda <- c(as.matrix(x))
  simCount <- matrix(mapply(function(y){rpois(1,y)},y=lambda), nrow = nrow(x), ncol = ncol(x))
  dimnames(simCount) <- dimnames(x)
  retrun(simCount)
})

>>>>

```{r roadInjuries6, message = FALSE, , dev=c('png'), eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
simRI <- lapply(getRoadInjuries(ITHIM.baseline), function(x){
  lambda <- c(as.matrix(x))
  simCount <- matrix(mapply(function(y){rpois(1,y)},y=lambda), nrow = nrow(x), ncol = ncol(x))
  dimnames(simCount) <- dimnames(x)
  return(simCount)
})
